\huge Tor's Usability for Censorship Circumvention

### 2016-04-20 pets2017-paper/pets2017-paper.tex
pass through limitations, future work, and discussion.

\begin{description}
\item{\bfseries Automate the configuration.} This sounds like a radical idea, but this wouldn't harm users today. Additionally, our study finds that most users would leak that they are using Tor when trying to circumvent an advanced censor. 
\item{\bfseries Ask about the risk.} Ask the users if they would be at risk if the process was automated, and automate the configuration process for all who are not at risk. The ones at risk will configure manually. The complication with this approach is that users may not be qualified to answer this question or may not trust Tor to answer honestly. 
\item{\bfseries Ask if users if they know what to do.} We ask users if they know how to configure a bridge and proxy, and automate the configuration process if they do not. However, there are ethical implications of making mistakes on behalf of the users if there is risk involved. 
\end{description}

@@

\section{Conclusion} 
We conducted a series of experiments to improve the Tor launcher configuration interface, which helps users circumvent censorship using Tor Browser. The qualitative user study interviews a screened 16 participants about their experience trying to circumvent mild, intermediate, and heavy censorship with the current interface, giving insight into common struggles, such as difficulty in answering technical questions, feeling unqualified to make technical choices, and not receiving feedback in the event of a failed configuration. This feedback is used to guide the redesign of the configuration interface.

>>>>

\begin{description}
\item{\bfseries Automate the configuration.} Complete automation and network probing sounds like a radical idea, but this wouldn't harm users today (as far as we know). Most users would leak that they are using Tor when trying to circumvent an advanced censor, since most first attempts to connect fail. 
\item{\bfseries Ask about the risk.} Ask the users if they would be at risk if the process was automated, and automate the configuration process for all who are not at risk. The ones at risk will configure manually. The complication with this approach is that users may not be qualified to answer this question or may not trust Tor to answer honestly. 
\item{\bfseries Ask if users if they know what to do.} We ask users if they know how to configure a bridge and proxy, and automate the configuration process if they do not. However, there are ethical implications of making mistakes on behalf of the users if there is risk involved. 
\end{description}

@@

\section{Conclusion} 
We conducted a series of experiments to improve the Tor 5.0.3 Tor launcher configuration interface, which helps users circumvent censorship using Tor. The qualitative user study interviews 16 pre-screened participants about their experience trying to circumvent mild, intermediate, and heavy censorship with the current interface, giving insight into common challenges in configuring a connection, such as confusing the necessity of bridges and proxies, assuming that a correct configuration was wrong due to a progress bar bug, and not knowing what to do on failure. This feedback is used to guide the redesign of the configuration interface.
